Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsection{Imprecision}
In this dissertation, we study two types of side-channel leakage code patterns. The intuition is that the target application shows different control flows or data flows when it processes different sensitive input data. We refer them as \textit{secret-dependent control flow transfers} and \textit{secret-dependent data accesses}. Unlike previous work, our tool works on the machine code, which is more precise than previous tools that work on the source code or the intermediate representation.
\subsubsection{Control Flow}
\begin{figure}[ht]
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.0\textwidth, frame=none]
int example1(uint8_t k, uint32_t m) { 
  uint32_t b = (k & m) >> 7; // m = 0
  if (b) {
    ...    // Branch 1
  } else {
    ...    // Branch 2
  }
  ...
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_k]    
and   eax, [addr_me] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
  \end{minipage}\caption*{(a) A False Negative}

>>>>

\subsection{Imprecision}
In this dissertation, we study two types of side-channel leakage code patterns. The intuition is that the target application shows different control flows or data flows when it processes different sensitive input data. We refer them as \textit{secret-dependent control flow transfers} and \textit{secret-dependent data accesses}. Unlike previous work, our tool works on the machine code, which is more precise than previous tools that analyze the source code or the intermediate representation.
\subsubsection{Control Flow}
\begin{figure}[ht]
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.0\textwidth, frame=none]
int example1(uint8_t k, uint32_t m) { 
  uint32_t b = (k & m) >> 7; // m = 0
  if (b) {
    ...    // Branch 1
  } else {
    ...    // Branch 2
  }
  ...
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_k]    
and   eax, [addr_me] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
  \end{minipage}\caption*{(a) A False Negative}
